---
title: "By the numbers"
output: html_document
date: "2024-05-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#install and run packages
```{r}
rm(list=ls())

#install.packages("rvest")
library(rvest)
#install.packages("pdftools")
library(pdftools)
library(tidyverse)


```

#Pulling and downloading the pdf from online for Northern Sierra precpipitation
```{r}

#URL of pdf file

# ***** need to see if this pdf updates everyday with the same URL *******
northern_pdf_url <- "https://cdec.water.ca.gov/cgi-progs/products/PLOT_ESI.pdf"


#pathway to where you want the pdf to be saved
#can eventaully make the name of the pdf with the date it is downloaded

northern_pdf_file<-"C:/Users/jweidenfeld/Desktop/Rprojects/By_The_Numbers/data_output/northern_sierra.pdf"



# Download the PDF file

# The "wb" mode is typically used when downloading non-text files, such as images, PDFs, or other binary files. It tells R to open the file in binary mode, which is necessary for correctly handling binary data
download.file(northern_pdf_url, northern_pdf_file, mode = "wb")

# Extract text from the PDF
northern_pdf_text <- pdf_text(northern_pdf_file)

# Print the extracted text
print(northern_pdf_text)

```

#Pulling the 'current' precipitation for Northern Sierra (using that starts on line 79)
```{r}

# Assuming pdf_file contains the path to the PDF file you downloaded earlier
# Extract text from the PDF
pdf_text <- pdf_text(pdf_file)

# Print the next four characters following "Current:" in each sentence
if (length(pdf_text) > 0) {
  for (sentence in pdf_text) {
    pattern <- "(?i)Current:\\s?(.{4})"
    next_four <- regmatches(sentence, regexpr(pattern, sentence, perl = TRUE))
    if (length(next_four) > 0) {
      print(paste("Current:", next_four))
    } else {
      print("Next four characters after 'Current:' not found.")
    }
  }
} else {
  print("No text extracted from the PDF.")
}


```

#Pulling the 'current' precipitation inches for Northern Sierra
```{r}
northern_next_four_values <- c()

# Extract text from the PDF file
northern_pdf_text <- pdf_text(northern_pdf_file)

# Print the next four characters following "Current:" in each sentence
if (length(northern_pdf_text) > 0) {
  for (sentence in northern_pdf_text) {
    pattern <- "(?i)Current:\\s?(.{4})"
    northern_next_four <- regmatches(sentence, regexpr(pattern, sentence, perl = TRUE))
    if (length(northern_next_four) > 0) {
      # Append the value of next_four to the vector
      northern_next_four_values <- c(northern_next_four_values, northern_next_four)
      print(paste("Current:", northern_next_four))
    } else {
      print("Next four characters after 'Current:' not found.")
    }
  }
} else {
  print("No text extracted from the PDF.")
}

# Print the values of next_four_values
print(northern_next_four_values)


```
#Northern Sierra
# Pulling out percent average for this date
```{r}
#create an empty vector
northern_next_four_values_average <- c()

# Extract text from the PDF file
northern_pdf_text <- pdf_text(northern_pdf_file)

# Print the next four characters following "Current:" in each sentence
if (length(northern_pdf_text) > 0) {
  for (sentence in northern_pdf_text) {
    pattern <- "(?i)Percent of Average for this Date:\\s?(.{4})"
    northern_next_four <- regmatches(sentence, regexpr(pattern, sentence, perl = TRUE))
    if (length(next_four) > 0) {
      # Append the value of next_four to the vector
      northern_next_four_values_average <- c(northern_next_four_values_average, northern_next_four)
      print(paste("Percent of Average for this Date:", northern_next_four_values_average))
    } else {
      print("Next four characters after 'Percent of Average for this Date:' not found.")
    }
  }
} else {
  print("No text extracted from the PDF.")
}

# Print the values of next_four_values
print(northern_next_four_values_average)


```

#Central Sierra precipitation
#Pulling and downloading the pdf from online 
```{r}

#URL of pdf file

# ***** need to see if this pdf updates everyday with the same URL *******
central_ppt_pdf_url <- "https://cdec.water.ca.gov/cgi-progs/products/PLOT_FSI.pdf"


#pathway to where you want the pdf to be saved
#can eventaully make the name of the pdf with the date it is downloaded
central_ppt_pdf_file2<-"C:/Users/jweidenfeld/Desktop/Rprojects/By_The_Numbers/data_output/central_sierra2.pdf"

# Download the PDF file

# The "wb" mode is typically used when downloading non-text files, such as images, PDFs, or other binary files. It tells R to open the file in binary mode, which is necessary for correctly handling binary data
download.file(central_ppt_pdf_url, central_ppt_pdf_file2, mode = "wb")

# Extract text from the PDF
central_pdf_text <- pdf_text(central_ppt_pdf_file2)

# Print the extracted text
print(central_pdf_text)

```
#Central Sierra
#PUlling out Percent average
```{r}
#create an empty vector
central_next_four_values <- c()

# Extract text from the PDF file
central_pdf_text <- pdf_text(central_ppt_pdf_file)

# Print the next four characters following "Current:" in each sentence
if (length(central_pdf_text) > 0) {
  for (sentence in central_pdf_text) {
    pattern <- "(?i)Percent of Average for this Date:\\s?(.{4})"
    next_four <- regmatches(sentence, regexpr(pattern, sentence, perl = TRUE))
    if (length(next_four) > 0) {
      # Append the value of next_four to the vector
      central_next_four_values <- c(central_next_four_values, next_four)
      print(paste("Percent of Average for this Date:", next_four))
    } else {
      print("Next four characters after 'Current:' not found.")
    }
  }
} else {
  print("No text extracted from the PDF.")
}

# Print the values of next_four_values
print(central_next_four_values)

```

# Central Sierra
# #Pulling the 'current' precipitation inches for Central Sierra
```{r}
#create and empty vector 
central_current_ppt <- c()
# Extract text from the PDF file
central_pdf_text <- pdf_text(central_ppt_pdf_file)

# Print the next four characters following "Current:" in each sentence
if (length(central_pdf_text) > 0) {
  for (sentence in central_pdf_text) {
    pattern <- "(?i)Current:\\s?(.{4})"
    next_four <- regmatches(sentence, regexpr(pattern, sentence, perl = TRUE))
    if (length(next_four) > 0) {
      # Append the value of next_four to the vector
      central_current_ppt <- c(central_current_ppt, next_four)
      print(paste("Current:", next_four))
    } else {
      print("Next four characters after 'Current:' not found.")
    }
  }
} else {
  print("No text extracted from the PDF.")
}

# Print the values of next_four_values
print(central_current_ppt)

```

##########################################################
                      # SNOW PACK #

```{r}
#URL of pdf file

# ***** need to see if this pdf updates everyday with the same URL *******
snow_pack_pdf_url <- "https://cdec.water.ca.gov/cgi-progs/products/swccond.pdf"


#pathway to where you want the pdf to be saved
#can eventaully make the name of the pdf with the date it is downloaded
snow_pack_pdf_file<-"C:/Users/jweidenfeld/Desktop/Rprojects/By_The_Numbers/data_output/snow_pack.pdf"

# Download the PDF file

# The "wb" mode is typically used when downloading non-text files, such as images, PDFs, or other binary files. It tells R to open the file in binary mode, which is necessary for correctly handling binary data
download.file(snow_pack_pdf_url, snow_pack_pdf_file, mode = "wb")

# Extract text from the PDF
snow_pack_pdf_text <- pdf_text(snow_pack_pdf_file)

# Print the extracted text
print(snow_pack_pdf_text)


```



#North Snow average snow pack
```{r}
# Define the pattern to match the line containing "NORTH" and the associated percentages
pattern <- "(?i)NORTH\\s{2,}(\\d+%).*?(\\d+%)"

# Extract the "NORTH" section
north_match <- regmatches(snow_pack_pdf_text, regexec(pattern, snow_pack_pdf_text, perl = TRUE))

# Check if the "NORTH" section is found
if (length(north_match) > 0) {
  # Extract both percentages from the matched text
  north_percentages <- regmatches(north_match[[1]], gregexpr("\\d+%", north_match[[1]]))[[1]]
  
  # Print the extracted percentage
  if (length(north_percentages) >= 2) {
    print(paste("NORTH", north_percentages[2], "of percent avg. to date snow pack"))
  } else {
    print("Second percentage in the 'NORTH' section not found.")
  }
} else {
  print("NORTH section not found.")
}

```
#north snow water equivalent
```{r}

# Define the pattern to match the line containing the snow water equivalent information
pattern <- "(?i)Average snow water equivalent \\(Inches\\)\\s+\\d+\\.\\d+"

# Extract the line containing snow water equivalent information
snow_water_line <- regmatches(snow_pack_pdf_text, regexpr(pattern, snow_pack_pdf_text, perl = TRUE))

# Check if the line is found
if (length(snow_water_line) > 0) {
  print(snow_water_line)
} else {
  print("Snow water equivalent information not found.")
}


```
#Central % Snow average snow pack
```{r}
# Define the pattern to match the line containing "NORTH" and the associated percentages
pattern <- "(?i)CENTRAL SIERRA\\s{2,}(\\d+%).*?(\\d+%)"

# Extract the "CENTRAL SIERRA" section
central_match <- regmatches(snow_pack_pdf_text, regexec(pattern, snow_pack_pdf_text, perl = TRUE))

# Check if the "CENTRAL SIERRA" section is found
if (length(central_match) > 0) {
  # Extract both percentages from the matched text
  central_percentages <- regmatches(central_match[[1]], gregexpr("\\d+%", central_match[[1]]))[[1]]
  
  # Print the extracted percentage
  if (length(central_percentages) >= 2) {
    print(paste("CENTRAL SIERRA", central_percentages[2], "of percent avg. to date snow pack"))
  } else {
    print("Second percentage in the 'CENTRAL SIERRA' section not found.")
  }
} else {
  print("CENTRAL SIERRA section not found.")
}


```
#Central snow water equivalent
```{r}
# Find the position of "Central Sierra" in the text
central_sierra_position <- regexpr("(?i)Central Sierra", snow_pack_pdf_text)

# If "Central Sierra" is found, find the position of "Average snow water equivalent (Inches)" after it
if (central_sierra_position > 0) {
  # Get the substring starting from the position of "Central Sierra"
  substring_after_central <- substring(snow_pack_pdf_text, central_sierra_position)
  
  # Find the position of "Average snow water equivalent (Inches)" within the substring
  snow_water_position <- regexpr("(?i)Average snow water equivalent \\(Inches\\)", substring_after_central)
  
  # If "Average snow water equivalent (Inches)" is found, extract the numeric value following it
  if (snow_water_position > 0) {
    # Get the substring starting from the position of "Average snow water equivalent (Inches)"
    snow_water_substring <- substring(substring_after_central, snow_water_position)
    
    # Extract the numeric value following "Average snow water equivalent (Inches)"
    snow_water_value <- regmatches(snow_water_substring, regexpr("\\d+\\.\\d+", snow_water_substring))
    
    # If a numeric value is found, print it
    if (length(snow_water_value) > 0) {
      print(snow_water_value)
    } else {
      print("Snow water equivalent value not found.")
    }
  } else {
    print("Average snow water equivalent information not found for Central Sierra.")
  }
} else {
  print("Central Sierra information not found.")
}


```
# State average snow pack: water year
```{r}

# Find the position of "State" in the text
state_position <- regexpr("(?i)State", snow_pack_pdf_text)

# If "State" is found, find the position of the numeric value after it
if (state_position > 0) {
  # Get the substring starting from the position of "State"
  substring_after_state <- substring(snow_pack_pdf_text, state_position)
  
  # Extract the numeric value following "State"
  snow_water_value <- regmatches(substring_after_state, regexpr("\\d+\\.\\d+", substring_after_state))
  
  # If a numeric value is found, print it
  if (length(snow_water_value) > 0) {
    print(snow_water_value)
  } else {
    print("Snow water equivalent value not found.")
  }
} else {
  print("State information not found.")
}

```
#Percent of normal for this date (%)
```{r}

# Find the position of "Statewide Average:" in the text
statewide_position <- regexpr("(?i)Statewide Average:", snow_pack_pdf_text)

# If "Statewide Average:" is found, find the position of the numeric value after it
if (statewide_position > 0) {
  # Get the substring starting from the position of "Statewide Average:"
  substring_after_statewide <- substring(snow_pack_pdf_text, statewide_position)
  
  # Extract both percentages from the matched text
  statewide_percentages <- regmatches(substring_after_statewide, gregexpr("\\d+%", substring_after_statewide))[[1]]
  
  # Print the second percentage
  if (length(statewide_percentages) >= 2) {
    print(statewide_percentages[2])
  } else {
    print("Second percentage after 'Statewide Average:' not found.")
  }
} else {
  print("Statewide Average information not found.")
}


```
                      




